DOpElib:\\ Differential Equations and Optimization Environment

### 2014-10-31 Examples/Documentation/introduction.tex
A bit more information on the flags and LD_LIBRARY_PATH for ipopt installation

>>>>

The installation is straighforward and has been tested on openSUSE 12.1
machines as well as on MAC. At the end of the installtion do not forget to
add ipopt to your {\tt LD\underline{ }LIBRARY\underline{ }PATH}:
\begin{lstlisting}
**************************************************************
                 Installation complete!
Add /home/..../dopelib-2.0/ThirdPartyLibs/ipopt/lib64
    to your $LD_LIBRARY_PATH variable
**************************************************************
\end{lstlisting}

### 2014-10-31 Examples/OPT/StatPDE/Example6/content.tex
A bit more information on the flags and LD_LIBRARY_PATH for ipopt installation

In addition the following functionals are evaluated:
\begin{gather*}
  \text{MidPoint: } u(0.5 ; 0.5)\\[2mm]
  \text{MeanValue: }\int_\Omega u
\end{gather*}

@@

\subsubsection{External optimization solver}
The problem is solved using the optimization library IPOPT that you can obtain for free. To use it 
a correct link to the ipopt library needs to be created in  {\tt DOpE/ThirdPartyLibs} by the name 
{\tt ipopt}, i.e., you should have the file
{\tt DOpE/ThirdPartyLibs/ipopt} pointing to the ipopt directory. If you have not done this you can compile the
example but when running the example you will only get an error message like\\
{\tt Warning: During execution of `Reduced\underline{ }IpoptAlgorithm::Solve`\\ the following Problem occurred!\\
To use this algorithm you need to have IPOPT installed! \\To use this set the WITH\underline{ }IPOPT CompilerFlag.}

>>>>

In addition the following functionals are evaluated:
\begin{gather*}
  \text{MidPoint: } u(0.125 ; 0.75)\\[2mm]
  \text{MeanValue: }\int_\Omega |u|
\end{gather*}

@@

\subsubsection{External optimization solver}
The problem is solved using the optimization library IPOPT that you can obtain for free. To use it 
a correct link to the ipopt library needs to be created in  {\tt DOpE/ThirdPartyLibs} by the name 
{\tt ipopt}, i.e., you should have the file
{\tt DOpE/ThirdPartyLibs/ipopt} pointing to the ipopt directory. If you have not done this you can compile the
example but when running the example you will only get an error message like\\
{\tt Warning: During execution of `Reduced\underline{ }IpoptAlgorithm::Solve`\\ the following Problem occurred!\\
To use this algorithm you need to have IPOPT installed! \\To use this set the WITH\underline{ }IPOPT CompilerFlag.}
If you receive this message and have the ipopt installation complete, you
might have overseen to add ipopt to your {\tt LD\underline{ }LIBRARY\underline{ }PATH}:
\begin{lstlisting}
**************************************************************
                 Installation complete!
Add /home/..../dopelib-2.0/ThirdPartyLibs/ipopt/lib64
    to your $LD_LIBRARY_PATH variable
**************************************************************
\end{lstlisting}
